Neural Connectome of the Ctenophore Statocyst

### 2025-04-29 manuscript/Manuscript.qmd
Fig5

![**Figure 4. Differences in Balancer Cilia Movement Control Due to Variations in the Neural Circuit Pathways and Comparison of Neural Circuits Regulating Ciliary Movement**\
(A) Schematic diagram of differential interference contrast (DIC) microscopy setup for imaging balancer cilia movement. The microscope was tilted 90 degrees so that the stage was positioned vertically. A monochrome CMOS camera sensitive to near-infrared (NIR) light was used, synchronized with an 850 nm strobe light source. The movement of the balancer cilia was recorded using a 40× objective lens.\
(B) Kymograph patterns comparing the arrest and re-beat of balancer cilia movement. The left and right balancer cilia movements are compared in both the sagittal plane (left) and tentacular plane (right). The direction and length of the arrows indicate time.\
(C) Graph showing the time differences in the arrest and re-beat timing of the left and right balancer cilia. S and T represent the sagittal plane and tentacular plane, respectively.\
(D) Each neuron represented by a circle is color-coded to indicate putative homologous cell types involved in ciliary movement regulation. Ciliated cells are shown in gray. Synapses are indicated by arrows, with magenta representing synapses that induce ciliary arrest and blue representing synapses that induce ciliary re-beat or an increase in ciliary beating frequency.\
(Left) Gravity-sensing neural circuit of *M. leidyi*, as revealed in this study. Bridge cells (yellow squares) are suggested to be electrically coupled (indicated by yellow zigzag lines), implying their potential involvement in feedback mechanisms between neurons and ciliated cells.\
(Righr) Neural circuit regulating prototroch ciliary movement in *P. dumerilii*. Serotonergic neurons (Ser-h1 neurons, blue) activate ciliary movement, while cholinergic neurons (MC neurons, magenta) induce ciliary arrest. Arrows directed toward ciliated cells in the head prototroch are color-coded accordingly.](figures/Figure4.png)

@@

>>>>

![**Figure 4. Differences in Balancer Cilia Movement Control Due to Variations in the Neural Circuit Pathways**\
(A) Schematic diagram of differential interference contrast (DIC) microscopy setup for imaging balancer cilia movement. The microscope was tilted 90 degrees so that the stage was positioned vertically. A monochrome CMOS camera sensitive to near-infrared (NIR) light was used, synchronized with an 850 nm strobe light source. The movement of the balancer cilia was recorded using a 40× objective lens.\
(B) Kymograph patterns comparing the arrest and re-beat of balancer cilia movement. The left and right balancer cilia movements are compared in both the sagittal plane (left) and tentacular plane (right). The direction and length of the arrows indicate time.\
(C) Graph showing the time differences in the arrest and re-beat timing of the left and right balancer cilia. S and T represent the sagittal plane and tentacular plane, respectively.](figures/Figure4.png)

@@

![**Figure 5. Comparison of Neural Circuits Regulating Ciliary Movement**\
(A) Each neuron represented by a circle is color-coded to indicate putative homologous cell types involved in ciliary movement regulation. Ciliated cells are shown in gray. Synapses are indicated by arrows, with magenta representing synapses that induce ciliary arrest and blue representing synapses that induce ciliary re-beat or an increase in ciliary beating frequency.\
(Left) Gravity-sensing neural circuit of *M. leidyi*, as revealed in this study. Bridge cells (yellow squares) are suggested to be electrically coupled (indicated by yellow zigzag lines), implying their potential involvement in feedback mechanisms between neurons and ciliated cells.\
(Righr) Neural circuit regulating prototroch ciliary movement in *P. dumerilii*. Serotonergic neurons (Ser-h1 neurons, blue) activate ciliary movement, while cholinergic neurons (MC neurons, magenta) induce ciliary arrest. Arrows directed toward ciliated cells in the head prototroch are color-coded accordingly.](figures/Figure5.png)
